# Package installation

## Run the below code to install the packages for this workshop.

```{r}
  # This make take a few minutes to complete
  install.packages(c(
                     # Visualizations
                     "ggplot2", "cowplot",
                     # Data reshaping
                     "reshape2", 
                     # Create .html, .docx, .pdf, slideshows, etc.
                     "rmarkdown", "knitr",
                     # Clustering
                     "ape", "pvclust", 
                     # Map stuff
                     "ggmap", 
                     # If we have time...
                     "sf", "units", "tmap", "nngeo", "raster"), 
                     # Install package dependencies
                     dependencies = TRUE)
```

If asked "Do you want to install from sources the packages which need compilation? (Yes/no/cancel)" type no and press enter

If you are asked to update any packages, type 1 and press enter

## `library` these packages to import them into our current R session

```{r}
suppressMessages(suppressWarnings({  
  library(ggplot2)
  library(cowplot)
  library(reshape2)
  library(rmarkdown)
  library(knitr)
  library(ape)
  library(pvclust)
  library(ggmap)
  library(sf)
  library(units)
  library(tmap)
  library(nngeo)
  library(raster)
}))
```

>NOTE: If ggmap does not install properly or otherwise causes errors, try:  
devtools::install_github("dkahle/ggmap")
