# Basics and data import

## 1. Navigating RStudio
- Top left window pane = input (script or markdown); enter your code here - it is easy to save :^)  
- Bottom right = output (console); noodle around down here - this is difficult to save :^(  
- Upper right = global environment (saved variables/data live here)  
- Bottom right = File structure, plots, package installation, help  

## 2. Variable assignment

Variable assignment is how we save data in R's memory. Variables are simply placeholders for data! These variables live in the global environment.

```{r}



```

## 3. The data

The data can be found in the data-raw folder. There are three Aquastat datasets and one GBIF dataset.

- [Aquastat datasets for Mexico, USA, and Canada](http://www.fao.org/nr/water/aquastat/data/query/index.html?lang=en)  

Load the Aquastat datasets
```{r}



```

- The [Global Biodiversity Information Facility (GBIF)](https://www.gbif.org/occurrence/download?dataset_key=8a863029-f435-446a-821e-275f4f641165) (Observation.org, Nature data from the Netherlands simple occurrences; login required)
- GBIF data user agreement: https://www.gbif.org/terms/data-user  
- GBIF citation guidelines: https://www.gbif.org/citation-guidelines  
- citation: GBIF.org (23 October 2019) GBIF Occurrence Download   https://doi.org/10.15468/dl.jgjalb  

Load the gbif dataset (subset of first 1000 rows only)
```{r}



```

> NOTE: you can also use the "Import Dataset" button on the Environment tab to import the data if read.csv does not make any sense! 

Inspect the Aquastat datasets

```{r}


```

`rbind` the Aquastat datasets into one! 

```{r}



```

"melt" the single Aquastate dataset from wide to long format

```{r}

```

Inspect the GBIF dataset

```{r}



```

Save these variables for future use :) 
```{r}



```
