# gg Visualizations

Load the Aquastat data by loading the .RData file from the end of 2-data-import.Rmd

```{r}

```

## 6. Data visualization with ggplot2

ggplot2 works in layers - each time you want to add something, add another layer by typing the `+` symbol at the end of a line of runnable code - this keeps the chain of layers looking like one single image.  

You need three things to make a ggplot:  
1. data  
2. "aes"thetics - here you define your x and y coordinate systems, map colors to points, etc.  
3. "geom_"s - how the data should be represented on the plot (points, boxes, bars, lines, ribbons, polygons, etc.)  

>Don't forget! ggplot2 is the package name, but ggplot is the function call!

### Creating the base layer

```{r}



```

### Histogram

A histogram is useful to visualize the distribution of a single continuous (i.e., numeric or integer) variable

```{r}



```

### Boxplot

A boxplot can also be used to visualize the distribution of a single continuous variable. However, boxplots are handy because we can do this for multiple levels of a factor

```{r}



```

### Scatterplot

A scatterplot is useful to visualize two continuous variables

```{r}



```

##### Facetting

Facetting is useful when you want to turn an overlaid graph into separate panels for each level of a factor. 

```{r}



```

##### Subplotting

The cowplot package allows you to add whichever sub-figures you choose a single figure. 

```{r}


```
